Using the Paleocore R API Interface
========================================================

This demo shows the functionality of the PaleoCore API using the Turkana dataset as an example. 

## Preliminaries
The PaleocoreR package is not yet on CRAN, so you cannot install it using the normal R package installation method.  Instead you can use a function called `install_github()` from the `devtools` package to install the package from the [paleocoreR github page](http://paleocore.github.com/paleocoreR), as shown below.

```{r echo = TRUE, warning=FALSE, message=FALSE}
library(devtools)
install_github("paleocore/paleocoreR")
library(paleocoreR)

#also load the ggplot2 package for graphing.  If this package is not installed already you can try
#install.packages("ggplot2")
library(ggplot2)
```
## See which fields can be filtered on in the Turkana dataset

```{r getfilters}
getFilters(project="turkana")
```


## Pull down all the bovids

```{r getbovids}
bovids <- getPCdata(project = "turkana", family="Bovidae", limit=0)
str(bovids)
```

## Plot bovids by tribe
```{r plotbytribe,  fig.width=14, height=9}
qplot(data=bovids, x=tribe)
```


## Authentication

Some datasets require authentication (Turkana does not).  This R package provides a convenience function for storing your PaleoCore username and api_key for authentication.  If you have a paleocore login account, you can get your api_key at [http://paleocore.org/apikey](http://paleocore.org/apikey). If you need to create a login account please [contact the paleocore administrators](http://paleocore.org/about). 

```{r authentication}
setPCcredentials(username="proconsul", api_key="s93jsp9823jd83mw2md922d93kd73f23kdf23ld7")
```